Economic Theory of Fertility Explains Modern Natural Selection

### 2020-12-01 why-negative-selection.Rmd
Tweak _drake; add within-family regression on income (unused at present); add drake-runner script for job; remove parallelism again

```{r plot-siblings-townsend, fig.cap = "Selection effects in the parents' generation by Townsend deprivation score quintile", fig.align = "center"}

@@

res_townsend_parents %>% 
  mutate(
    `Townsend quintile` = sub("Quin71(\\d):.*", "\\1", term),
    add_n(`Townsend quintile`, "Quin71", dv = "n_sibs", data = famhist_townsend_71)
  ) %>% 
  standard_ggplot(`Townsend quintile`, n_regs = n_regs, score_col = score_name, order_idx = 5)

@@

We also check whether selection effects differ by socio-economic status in the
parents' generation. We have no information about parents' income, so we use
the 1971 Townsend deprivation score of respondents' birthplace as a proxy. Results
(Figure \@ref(fig:plot-siblings-townsend)) show the same pattern as for respondents:
effect sizes are larger and more significant in the most deprived areas.

@@

drake::loadd(res_all)
drake::loadd(res_age_flb)

@@

```{r plot-res-earn-educ, fig.cap = "Selection effects controlling for earnings in first job (estimated by median earnings from ASHE 2007 for the SOC2000 job code) and education (left education before 16, 16-18, or after 18). Raw effects are shown for comparison. Lines are 95% confidence intervals uncorrected for multiple testing."}

>>>>

```{r plot-siblings-townsend, fig.cap = "Selection effects in the parents' generation by area Townsend deprivation quintile", fig.align = "center"}

@@

res_townsend_parents %>% 
  mutate(
    `Townsend quintile` = sub("Quin71(\\d):.*", "\\1", term),
    `Townsend quintile` = add_n(`Townsend quintile`, "Quin71", dv = "n_sibs", 
                                  data = famhist_townsend_71)
  ) %>% 
  standard_ggplot(fill_col    = `Townsend quintile`,
                    n_regs    = n_regs, 
                    score_col = score_name, 
                    order_idx = 5
                  )

@@

We also check whether selection effects differ by socio-economic status in the
parents' generation. We have no information about parents' income, so we use the
1971 Townsend deprivation score of respondents' birthplace as a proxy
[@townsend1987deprivation]. Results (Figure \@ref(fig:plot-siblings-townsend))
show the same pattern as for respondents: effect sizes are larger and more
significant in the most deprived areas.

@@

drake::loadd(res_all)
drake::loadd(res_age_flb)
drake::loadd(ashe_income)

famhist <- add_ashe_income(famhist, ashe_income)

@@

```{r plot-res-earn-educ, fig.cap = "Selection effects controlling for earnings in first job (estimated by mean earnings from ASHE 2007 for the SOC2000 job code) and education (left education before 16, 16-18, or after 18). Raw effects are shown for comparison. Lines are 95% confidence intervals uncorrected for multiple testing."}
